A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-10-07 latex/main.tex
Good enough ripples pango X table

>>>>

\subsection*{Comparison with RIPPLES}

\begin{table}
\caption{RIPPLES pango X lineage events.} 
\label{tab:ripples_x_lineages}
\centering
\begin{scriptsize}

\begin{tabular}{lrrlrl}
\toprule
pango & in p4 & UShER desc & sc2ts class & clade diff & descendants \\
\midrule
XBR & $\checkmark$ & 1 & I & 0 & {XBR:1} \\
XM3 & $\checkmark$ & 1 & I & 0 & {XM:1} \\
XC & $\checkmark$ & 5 & I & 0 & {XC:5} \\
XBM & $\checkmark$ & 12 & I & 0 & {XBM:10, BF.3:2} \\
XS & $\checkmark$ & 17 & I & 0 & {XS:17} \\
XY &  & 23 & I & 0 & {XY:23} \\
XW &  & 32 & I & 0 & {XW:32} \\
XA & $\checkmark$ & 39 & I & 0 & {XA:39} \\
XL &  & 64 & I & 0 & {XL:64} \\
XBB &  & 6452 & I & 1 & {XBB:2361} \\
\midrule
XQ &  & 1 & II & 0 & {XAM:1} \\
XM & $\checkmark$ & 8 & II & 0 & {BA.2:4, XM:4} \\
Xx &  & 9 & II & 0 & {XAE:9} \\
Xx & $\checkmark$ & 18 & II & 0 & {XAC:18} \\
XQ &  & 21 & II & 0 & {XAM:21} \\
XE/XH &  & 1113 & II & 3 & {XE:1113} \\
\midrule
XB & $\checkmark$ & 411 & IV & 0 & {B.1:219, XB:192} \\
\midrule
NA & $\checkmark$ & 19 & NA & 45190 & {XAJ:18, BA.4:1} \\
NA &  & 20 & NA & 1061775 & {BA.1.15:1, XS:17, BA.1:1, BA.1.1:1} \\
NA & $\checkmark$ & 35 & NA & 7147 & {XBD:30, BA.2.75:5} \\
NA & $\checkmark$ & 36 & NA & 7146 & {XBD:30, XBR:1, BA.2.75:5} \\
NA &  & 1321 & NA & 340501 & {XE:1113, XH:2, XJ:68, XY:23, BA.2:82, XM:29,
XAL:3, XAF:1} \\
\bottomrule
\end{tabular}

\end{scriptsize}
\end{table}
